COG-ED Manuscript

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
BFs for MLM added

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

@@

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

@@

  # get Bayes factors ----------------------------------------------------------

  # the random factor needs to be a factor
  h2b_data$subject <- factor(h2b_data$subject)

  # H2b
  h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2b_BF <- h2b_full_BF / h2b_null_BF

  # H2c
  h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
                      data = h2b_data, whichRandom = 'subject')
  h2c_BF <- h2c_full_BF / h2c_null_BF
